### 2018-07-10 doc/plos/text/manuscript.tex
add figure 1 to draft
make preview figures larger
figure 2: all nowcasts

>>>>

% Don't include figures in the final version. This is just for preview.
\newgeometry{top=1.0in,left=1.0in,footskip=30pt}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_top.png}
  Figure 1 (top).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/sensor_heatmap_bottom.png}
  Figure 1 (bottom).
\end{figure}
\begin{figure}[p]
  \includegraphics[width=\textwidth]{../data/figures/all_nowcasts.png}
  Figure 2.
\end{figure}
